Cost- and Deadline-Constrained Provisioning for Scientific Workflow Ensembles in IaaS Clouds

### 2012-04-27 paper/paper.tex
Edit abstract to 150-word SC limit

Large-scale computational applications represented as scientific workflows, are
often grouped into ensembles composed of several inter-related workflows. In
this paper, we address a new and important problem concerning the efficient 
management of such ensembles under both budget and deadline constraints on 
Infrastructure-as-a-Service (IaaS) clouds. IaaS clouds are characterized by
on-demand resource provisioning capabilities and a pay-per-use model.  We discuss,
develop, and assess algorithms based on static and dynamic strategies for both
task scheduling and resource provisioning. We assume that the workflows within
an ensemble are prioritized by the user. We evaluate the algorithms via
simulation using a set of scientific workflow ensembles with a broad range of
budget and deadline parameters, taking into account uncertainties in task runtime
estimations, provisioning delays and failures. We find that the key 
factor determining the performance of an algorithm is its ability to decide which
workflows in an ensemble to admit or reject for execution. The results
show that the admission procedure based on workflow structure and estimates of
task runtimes can significantly improve the quality of solutions.

>>>>

Large-scale computational applications expressed as scientific workflows are
often grouped into ensembles of inter-related workflows. In this paper, we
address a new and important problem concerning the efficient  management of
such ensembles under budget and deadline constraints on  Infrastructure-
as-a-Service (IaaS) clouds. We discuss, develop, and assess algorithms based
on static and dynamic strategies for both task scheduling and resource
provisioning. We evaluate the algorithms via simulation using a set of
scientific workflow ensembles with a broad range of budget and deadline
parameters, taking into account uncertainties in task runtime estimations,
provisioning delays and failures. We find that the key factor determining the
performance of an algorithm is its ability to decide which workflows in an
ensemble to admit or reject for execution. Our results show that an admission
procedure based on workflow structure and estimates of task runtimes can
significantly improve the quality of solutions.
